---
title: "Independent Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
install.packages('randomForest')
install.packages('cowplot')
install.packages('parallel')
install.packages('foreach')
install.packages('doParallel')
install.packages('e1071', dependencies=TRUE)
```
#### Ill import the necessary libraries.
```{r}
library(doParallel)
library(parallel)
library(randomForest)
library(ggplot2)
library(cowplot)
library(magrittr)
library(caret)
library(ggcorrplot)
library(ggExtra)
theme_set(theme_classic())
options(warn = -1)
```


#### Ill first import the dataset and display the head of the dataset
```{r}
greg <- read.csv('http://bit.ly/IPAdvertisingData')
head(greg)
```
#### Ill then display the tail of the dataset
```{r}
  tail(greg)
```
#### I'll then check the rows of the dataset
```{r}
rownames(greg, do.NULL = TRUE, prefix = "row")

```
#### Ill then check the columns of the dataset
```{r}
colnames(greg, do.NULL = TRUE, prefix = "col")
```
#### I'll then check for missing values in the dataset
```{r}
sum(is.na(greg))
```
The output shows no missing values after summation

#### I'll then check for duplicates
```{r}
sum(duplicated(greg))
```
The output shows no duplicates.

## UNIVARIATIVE ANALYSIS

### Ill check for outliers in the dataset
```{r}
boxplot(greg)
```
Their is presence of outliers,ill not drop them






#### Ill then show distribution of age 
```{r}
hist(greg$Age)
```


#### Ill then show various distribution in the

#### dataset like income,gender,etc

```{r}
hist(greg$Male)
```


#### Ill then distribution of income in the dataset

```{r}
hist(greg$Daily.Time.Spent.on.Site)
```
## Bivariate Analysis


#### Ill then use the plot_grid() function which  provides a simple 

#### interface for arranging plots into a grid and adding labels to them.

```{r}
library(ggplot2)
plot1 <- ggplot(greg, aes(x = Age, y = Daily.Internet.Usage, color = Clicked.on.Ad)) + geom_point(size = 3) +
  theme(text = element_text(size = 10), axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))
plot_grid(plot1)
```
```{r}
plot2 <- ggplot(greg, aes(x = Daily.Time.Spent.on.Site, y=Daily.Internet.Usage, color=Clicked.on.Ad)) + geom_point(size=3)+
  theme(text = element_text(size=10) ,axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))
plot_grid(plot2)
```
```{r}
plot3 <- ggplot(greg, aes(x = Age, y = Area.Income, color=Clicked.on.Ad)) + geom_point(size=3)+
  theme(text = element_text(size=10) ,axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))
plot_grid(plot3)
```
```{r}

plot4 <- ggplot(greg, aes(x = Area.Income, y = Daily.Internet.Usage, color = Clicked.on.Ad)) + geom_point(size=3)+
  theme(text = element_text(size=10) ,axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))
plot_grid(plot4)
```
## Modelling

##### I'll first split the dataset into train and test set
```{r}
greg$Clicked.on.Ad = as.factor(greg$Clicked.on.Ad)
training1 <- createDataPartition(y = greg$Clicked.on.Ad, p = .75, list = FALSE)
```
```{r}
training <- greg[training1,]
testing  <- greg[-training1,]
```
```{r}
cluster <- makeCluster(detectCores() - 1) 
registerDoParallel(cluster)
controlknn <- trainControl(method = "repeatedcv", number = 10, repeats = 3, verboseIter = TRUE)
KNNall <- train(Clicked.on.Ad ~ .,data = training, method = "knn",trControl = controlknn,preProc = c("center", "scale"),tuneLength = 10)

```
```{r}
KNNall
```

